### 2017-01-02 test/eigenface2.Rmd
eigenface

M<- sapply(list.files("."), function(x){substr(x,1,5)})

@@

K<- 2

@@

plotFace(raw$mu[1,] + mFaces)
plotFace(raw$mu[2,]+ mFaces)

@@

adjustedRandIndex(raw$M,M)

@@

adjustedRandIndex(arcM$M,M)

plotFace(arcM$mu[1,]%*%arcM$EV+ mFaces)
plotFace(arcM$mu[2,]%*%arcM$EV+ mFaces)

>>>>

M<- sapply(list.files("."), function(x){substr(x,1,5)})
faces<- faces[,M=="Alvar"]

@@

K<- 4

@@

plotFace(raw$mu[1,] + mFaces)
plotFace(raw$mu[2,]+ mFaces)
plotFace(raw$mu[3,]+ mFaces)
plotFace(raw$mu[4,]+ mFaces)
# plotFace(raw$mu[5,]+ mFaces)
# plotFace(raw$mu[6,]+ mFaces)
# plotFace(raw$mu[7,]+ mFaces)
# plotFace(raw$mu[8,]+ mFaces)

@@

@@

plotFace(arcM$mu[1,]%*%arcM$EV+ mFaces)
plotFace(arcM$mu[2,]%*%arcM$EV+ mFaces)
plotFace(arcM$mu[3,]%*%arcM$EV+ mFaces)
plotFace(arcM$mu[4,]%*%arcM$EV+ mFaces)
